MSF_Groupwork-NBA_shotlog

### 2016-10-09 MSFGroupwork-NBAHotHand.Rmd
Add topic options based on today's discussions.
started cleaning up data (win/loss column)

---
title: "MSF_Groupwork-NBA_shotlog"
author: "Team_9"
output: html_document
---

@@

###Introduction
I   What is your theme or research question?

###Theory
I   What do you expect to find?

>>>>

---
title: "MSF_Groupwork-NBA_shotlog"
author: "Team_9"
output: html_document  ---
  title: "MSF_Groupwork-NBA_shotlog"
author: "Team_9"
output: html_document
---

@@

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory  
b. Defender Proximity Analysis  
c. Shot Clock Pressure  
d. Close Game Effect - Small Margin affecting the scoring rate  
e. Home Advantage (Alex is working in this point)  
f. Fatigue Effect (Quarter Heat Rate)  
g. Shooting Percentage  
h. Fatigue Effect (Number of Rest Day)  
i.

###Theory
I   What do you expect to find?
a.

###Data clean-up

```{r}
df<- read.csv("shot_logs.csv")  #assigning the dataframe to 'df' variables
attach(df) #telling R that this is the dataframe we'll be working with (eliminating the need to use df$ for variables)

```

```{r}

df[,W] <- as.character(df[,W])

for (i in 1:nrow(df)) {
  df[i,] <- as.character(ky[, i])
  if (df[i,"W"]="W") df[i,"W"]<- 1
  if (df[i,"W"]="L") df[i,"W"]<- 0
}

for (i in 1:(ncol(ky) - 1)){
  ky[, i] <- as.character(ky[, i])
  for (j in 1:nrow(ky)){
    if (ky[j, i] == "Strongly Agree") ky[j, i] <- 5
    if (ky[j, i] == "Agree") ky[j, i] <- 4
    if (ky[j, i] == "Neither Agree nor Disagree") ky[j, i] <- 3
    if (ky[j, i] == "Disagree") ky[j, i] <- 2
    if (ky[j, i] == "Strongly Disagree") ky[j, i] <- 1
  }
  ky[, i] <- as.numeric(ky[, i])
}

```

I   What would be the next steps?
---

###Introduction
I   What is your theme or research question?
a. Hot Hand Theory
b. Defender Proximity Analysis
c. Shot Clock Pressure
d. Close Game Effect - Small Margin affecting the scoring rate
e. Home Advantage
f. Fatigue Effect (Quarter Heat Rate)
g. Shooting Percentage
h. Fatigue Effect (Number of Rest Day)
i.

###Theory
I   What do you expect to find?
a.
